---
title: "Hoosier National Forest Landscape Assessment"
author: "Team LF"
---

<font size="4"> 
**These LANDFIRE-Powered Landscape Assessments allow users to start exploring trends, landscape conversion and natural resource management options. **

</font> 


## Goals of this quick demonstration

We will use [LANDFIRE](https://landfire.gov/){target="blank"} products to:

1. Map and summarize past and present ecosystems and ecosystem conditions
2. Explore historical disturbance regimes
3. Summarize patterns of change and management opportunities


The following charts, maps, and graphs are based on current LANDFIRE products, however they are intended only as a starting point for further analysis. 

This introduction will:

* provide context for the past and present ecosystem conditions for the Hoosier National Forest (within the proclamation boundary)
* demonstrate the power of data visualization to explore ecological patterns and functions using LANDFIRE products
* facilitate an understanding of historical and current conditions on a regional scale

## How to use this web report

* QAQC is ongoing
* Want to share this web app? Simply share the hyperlink
* All maps, input datasets and further assistance can be obtained by contacting the author, [Randy Swaty](mailto:rswaty@tnc.org){target="blank"}


## Assessment Location

Hoosier National Forest (within the proclamation boundary)


<br>

```{r libraries, message=FALSE, warning=FALSE, include=FALSE}


library(sf)
library(terra)
library(tidyverse)
library(tmap)
library(tmaptools)



```


```{r read shapefile, message=FALSE, warning=FALSE, include=FALSE}
#  read shape
shp <- st_read("data/hoosier_proc.shp") %>% 
  st_transform(crs = 5070) %>%
  st_union() %>%
  st_sf()
```

```{r locator map, message=FALSE, warning=FALSE, echo=FALSE}


# toggle tmap mode to interactive viewing
tmap_mode("view")

# create a quick interactive map
quickmap <- qtm(shp, 
                borders = "darkgreen", 
                fill = NULL, 
                check.and.fix = TRUE, 
                basemaps = 'https://server.arcgisonline.com/ArcGIS/rest/services/World_Topo_Map/MapServer/tile/{z}/{y}/{x}',
                title = 'Hoosier National Forest',)

quickmap



```


* All maps, input datasets and further assistance can be obtained by contacting the author, Nature Conservancy LANDFIRE ecologist [Randy Swaty](mailto:rswaty@tnc.org){target="blank"}.
* Review is ongoing.
* To share this web app, simply share the hyperlink.
* Toggle between dark and light display of this site in the upper right corner of the page.
* Learn more about LANDFIRE and The Nature Conservancy [here](about.qmd){target="blank}. 